\documentclass[a4paper,11pt]{article}
\usepackage[margin=2.2cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{array}
\usepackage{hyperref}

\title{OGS PETSc + OpenMP + MFront Build\\
np=1 \texorpdfstring{$\rightarrow$}{->} np=4 CTest Comparison Report}
\author{Automated run on \texttt{petsc-local-ki-test}}
\date{2026-04-18}

\begin{document}
\maketitle

\section*{Scope}
This report documents the requested workflow:
\begin{itemize}
\item Build OGS in Release with PETSc, OpenMP, and MFront enabled.
\item Auto-generate \texttt{-np4} variants from existing \texttt{mpirun -np 1} tests.
\item Execute baseline (\texttt{petsc\_np1\_source}) and generated (\texttt{petsc\_np4\_variant}) test slices.
\item Compare outcomes pairwise and record reproducibility/revert notes.
\end{itemize}

\section*{Step Log (Reversible Logical Steps)}
\subsection*{Step 1: Preflight environment}
\begin{itemize}
\item Tools found on path: \texttt{/opt/anaconda3/bin/mpicc}, \texttt{mpic++}, \texttt{mpirun}, \texttt{pkg-config}, \texttt{python3}.
\item Python: \texttt{3.13.12}.
\item MPI launcher: MPICH Hydra \texttt{4.3.2}.
\item Important environment quirk: \texttt{mpicc} wrapper compiler name was invalid; all configure/build calls required
\texttt{MPICH\_CC='xcrun clang'} and \texttt{MPICH\_CXX='xcrun clang++'}.
\end{itemize}

\subsection*{Step 2: Checkpoint A feature state}
Checkpoint A (already present at start of this continuation) was \texttt{5324bca7bb}, adding:
\begin{itemize}
\item \texttt{OGS\_ENABLE\_PETSC\_NP4\_VARIANTS} option (default OFF).
\item Initial np1\textrightarrow{}np4 auto-clone logic and labels.
\end{itemize}

During this execution, label and tester wiring were corrected in:
\begin{itemize}
\item \texttt{scripts/cmake/test/AddTest.cmake}
\item \texttt{scripts/cmake/test/OgsTest.cmake}
\end{itemize}
Fixes applied:
\begin{itemize}
\item \texttt{petsc\_np1\_source} and \texttt{petsc\_np4\_variant} are now mutually exclusive.
\item np4 tester variants now use \texttt{-np4} output directories and carry \texttt{petsc\_np4\_variant}.
\end{itemize}

\subsection*{Step 3: Configure/build (Release PETSc + OpenMP + MFront)}
Configured with PETSc+MFront+OpenMP and np4 variants enabled, including PETSc batch mode:
\begin{verbatim}
MPICH_CC='xcrun clang' MPICH_CXX='xcrun clang++' /opt/anaconda3/bin/cmake \
  --preset release-petsc \
  -DOGS_ENABLE_PETSC_NP4_VARIANTS=ON
\end{verbatim}

Build strategy (to avoid unrelated unit-test blockage):
\begin{itemize}
\item Built runtime target: \texttt{cmake --build --preset release-petsc --target ogs}
\item Built tester tool: \texttt{cmake --build --preset release-petsc --target vtkdiff}
\end{itemize}

Execution-time build enablers applied in code:
\begin{itemize}
\item Serial-HDF5 fallback enabled for PETSc builds when \texttt{H5Pset\_fapl\_mpio} is unavailable.
\item XDMF MPI file I/O calls guarded by \texttt{H5\_HAVE\_PARALLEL} to keep non-parallel HDF5 paths buildable.
\item MGIS MFront behaviour CMake module included explicitly when command registration is missing.
\item System GTest preference added (with \texttt{autocheck} include setup) to avoid conda-header conflicts in this environment.
\end{itemize}

\subsection*{Step 4: Registration validation}
Validated labels and 1:1 mapping:
\begin{verbatim}
np1=94 np4=94 both=0
\end{verbatim}

\subsection*{Step 5: Execution passes}
Because MPICH teardown hung on this host without launcher overrides, ctest runs used:
\begin{verbatim}
HYDRA_LAUNCHER=fork HYDRA_IFACE=lo0
\end{verbatim}

Executed commands:
\begin{verbatim}
ctest -L petsc_np1_source --output-on-failure --progress \
      --output-junit /tmp/petsc_np1_source.junit.xml

ctest -L petsc_np4_variant --output-on-failure --progress \
      --output-junit /tmp/petsc_np4_variant.junit.xml
\end{verbatim}

Outcomes:
\begin{itemize}
\item Baseline (\texttt{petsc\_np1\_source}): 94/94 passed.
\item np4 variants (\texttt{petsc\_np4\_variant}): 0/94 passed, 94/94 failed.
\item Pair summary: 94 PASS\textrightarrow{}FAIL transitions.
\end{itemize}

Primary np4 failure cause: missing partitioned mesh binaries
(\texttt{*\_partitioned\_msh\_cfg4.bin}) required by MPI read paths. Tester
failures then cascade when np4 output files are absent.

\subsection*{Step 6: Reporting artefacts}
Generated:
\begin{itemize}
\item \texttt{Documentation/petsc\_np4\_comparison.csv}
\item \texttt{Documentation/petsc\_np4\_comparison\_rows.tex}
\item \texttt{Documentation/petsc\_np4\_summary.json}
\item this report: \texttt{Documentation/petsc\_np4\_report.tex}
\end{itemize}

\section*{Pairwise Comparison Table}
\footnotesize
\setlength{\LTleft}{0pt}
\setlength{\LTright}{0pt}
\begin{longtable}{p{0.36\linewidth} l r l r r r p{0.18\linewidth}}
\toprule
Baseline test & B status & B time [s] & np4 status & np4 time [s] & $\Delta$ [s] & ratio & np4 reason \\
\midrule
\endfirsthead
\toprule
Baseline test & B status & B time [s] & np4 status & np4 time [s] & $\Delta$ [s] & ratio & np4 reason \\
\midrule
\endhead
\input{petsc_np4_comparison_rows.tex}
\bottomrule
\end{longtable}
\normalsize

\section*{Reproducibility and Revert Notes}
\begin{itemize}
\item Rebuild/retest from this state by re-running the commands in Step 5.
\item Revert this report tooling/checkpoint-B changes with:
\begin{verbatim}
git restore --source=HEAD~1 -- Documentation/petsc_np4_report.tex \
  Documentation/petsc_np4_comparison.csv \
  Documentation/petsc_np4_comparison_rows.tex \
  Documentation/petsc_np4_summary.json \
  scripts/test/generate_petsc_np4_report.py \
  scripts/cmake/test/AddTest.cmake \
  scripts/cmake/test/OgsTest.cmake
\end{verbatim}
\item The runtime workaround \texttt{HYDRA\_LAUNCHER=fork HYDRA\_IFACE=lo0} is host-specific and was only used for test execution.
\end{itemize}

\end{document}
